E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-05 abstract.tex
abstract done

\begin{abstract}
	E-Mail header injection vulnerability is a class of vulnerability that can occur in web applications that use user input to construct e-mail messages. E-Mail injection is possible when the mailing script fails to check for the presence of e-mail headers in user input (either form fields or URL parameters). The vulnerability exists in the reference implementation of the built-in \dq{mail} functionality in popular languages like PHP, Java, Python, and Ruby\@. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an E-Mail message, allowing an attacker to completely alter the content of the e-mail.
	\paragraph{}
	This thesis develops a scalable mechanism to automatically detect E-Mail Header Injection vulnerability and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the Internet. Using a black-box testing approach, the system crawled \urls\ URLs to find URLs which contained form fields. \forms\ such forms were found by the system, of which \emailforms\ forms contained e-mail fields. The system used this data feed to discern the forms that could be fuzzed with malicious payloads. Amongst the \fuzzed\ forms tested, \recd\ forms were found to be injectable with more malicious payloads. The system tested \malfuzzed\ of these, and was able to find \success\ vulnerable URLs across \domains\ domains, which proves that the threat is widespread and deserves future research attention.

\end{abstract}

>>>>

\begin{abstract}
	E-Mail header injection vulnerability is a class of vulnerability that can occur in web applications that use user input to construct e-mail messages. E-Mail injection is possible when the mailing script fails to check for the presence of e-mail headers in user input (either form fields or URL parameters). The vulnerability exists in the reference implementation of the built-in \dq{mail} functionality in popular languages like PHP, Java, Python, and Ruby\@. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an E-Mail message, allowing an attacker to completely alter the content of the e-mail.

	This thesis develops a scalable mechanism to automatically detect E-Mail Header Injection vulnerability and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the Internet. Using a black-box testing approach, the system crawled \urls\ URLs to find URLs which contained form fields. \forms\ such forms were found by the system, of which \emailforms\ forms contained e-mail fields. The system used this data feed to discern the forms that could be fuzzed with malicious payloads. Amongst the \fuzzed\ forms tested, \recd\ forms were found to be injectable with more malicious payloads. The system tested \malfuzzed\ of these, and was able to find \success\ vulnerable URLs across \domains\ domains, which proves that the threat is widespread and deserves future research attention.
\end{abstract}

### 2016-05-05 paper.tex
abstract done

\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
\usepackage{color}
\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}

@@

	\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
		Format\titlenote{(Produces the permission block, and
			copyright information). For use with
			SIG-ALTERNATE.CLS. Supported by ACM.}}
	\subtitle{[Extended Abstract]
		\titlenote{A full version of this paper is available as
			\textit{Author's Guide to Preparing ACM SIG Proceedings Using
				\LaTeX$2_\epsilon$\ and BibTeX} at
			\texttt{www.acm.org/eaddress.htm}}}
	%
	% You need the command \numberofauthors to handle the 'placement
	% and alignment' of the authors beneath the title.
	%
	% For aesthetic reasons, we recommend 'three authors at a time'
	% i.e. three 'name/affiliation blocks' be placed beneath the title.
	%
	% NOTE: You are NOT restricted in how many 'rows' of
	% "name/affiliations" may appear. We just ask that you restrict
	% the number of 'columns' to three.
	%
	% Because of the available 'opening page real-estate'
	% we ask you to refrain from putting more than six authors
	% (two rows with three columns) beneath the article title.
	% More than six makes the first-page appear very cluttered indeed.
	%
	% Use the \alignauthor commands to handle the names
	% and affiliations for an 'aesthetic maximum' of six authors.
	% Add names, affiliations, addresses for
	% the seventh etc. author(s) as the argument for the
	% \additionalauthors command.
	% These 'additional authors' will be output/set for you
	% without further effort on your part as the last section in
	% the body of your article BEFORE References or any Appendices.

@@

	\maketitle
	\begin{abstract}
		This paper provides a sample of a \LaTeX\ document which conforms,
		somewhat loosely, to the formatting guidelines for
		ACM SIG Proceedings. It is an {\em alternate} style which produces
		a {\em tighter-looking} paper and was designed in response to
		concerns expressed, by authors, over page-budgets.
		It complements the document \textit{Author's (Alternate) Guide to
			Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
		This source file has been written with the intention of being
		compiled under \LaTeX$2_\epsilon$\ and BibTeX.

		The developers have tried to include every imaginable sort
		of ``bells and whistles", such as a subtitle, footnotes on
		title, subtitle and authors, as well as in the text, and
		every optional component (e.g. Acknowledgments, Additional
		Authors, Appendices), not to mention examples of
		equations, theorems, tables and figures.

		To make best use of this sample document, run it through \LaTeX\
		and BibTeX, and compare this source code with the printed
		output produced by the dvi file. A compiled PDF version
		is available on the web page to help you with the
		`look and feel'.
	\end{abstract}

@@

	\begin{figure}
		\centering
		%\includegraphics{fly.eps}
		\caption{A sample black and white graphic.}
	\end{figure}

>>>>

\usepackage[square,numbers]{natbib}
\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
\usepackage{color}
\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}

@@

	\title{E-jection fraction - Tracking how your website pumps out E-Mails}
	%
	% You need the command \numberofauthors to handle the 'placement
	% and alignment' of the authors beneath the title.
	%
	% For aesthetic reasons, we recommend 'three authors at a time'
	% i.e. three 'name/affiliation blocks' be placed beneath the title.
	%
	% NOTE: You are NOT restricted in how many 'rows' of
	% "name/affiliations" may appear. We just ask that you restrict
	% the number of 'columns' to three.
	%
	% Because of the available 'opening page real-estate'
	% we ask you to refrain from putting more than six authors
	% (two rows with three columns) beneath the article title.
	% More than six makes the first-page appear very cluttered indeed.
	%
	% Use the \alignauthor commands to handle the names
	% and affiliations for an 'aesthetic maximum' of six authors.
	% Add names, affiliations, addresses for
	% the seventh etc. author(s) as the argument for the
	% \additionalauthors command.
	% These 'additional authors' will be output/set for you
	% without further effort on your part as the last section in
	% the body of your article BEFORE References or any Appendices.

@@

	\maketitle
	\input{abstract}

@@

	\begin{figure}
		\centering
		%\includegraphics{System/fuzzer_design}
		\caption{A sample black and white graphic.}
	\end{figure}
